A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 main.tex
fix quotes

\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa ~University},
\city{Ume\aa}, \postcode{901 87}, \country{Sweden}}

@@

\begin{table}
\centering
\caption{Comparison of AFT Models across all hardware and datasets. \acrshort{aic}~and~\acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred. Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
\label{tab:aft_summary}
\begin{tabular}{lrrrrrrrr}
\toprule
             & AIC              & BIC & Conc & Test Conc & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull      & $-2.11\cdot10^4$ & $-2.11\cdot10^4$ & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
Log Logistic & $-2.18\cdot10^4$ & $-2.18\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
Log Normal   & $-2.25\cdot10^4$ & $-2.25\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}
\begin{figure*}[tph!]
    \centering
        \includegraphics[width=.49\linewidth]{plots/combined/weibull_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_qq.pdf}
    \caption{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $. A model that fits this cubic spline exactly would be a diagonal line at $y=x$. The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}
    \label{fig:qq}
\end{figure*}

>>>>

\affil*[1]{\orgdiv{Department of Computing Science}, \orgname{Ume\aa{}~University},
\city{Ume\aa}, \postcode{901 87}, \country{Sweden}}

@@

\begin{table}
\centering
\caption{
    Comparison of AFT Models across all hardware and datasets. 
    \acrshort{aic}~and~\acrshort{bic} are measures of goodness-of-fit, with a smaller value being preferred. 
    Concordance (Conc) is a value between 0 and 1 that reflects how what proportion of events (failures) can be explained by the model. 
    \acrshort{ici} measures the average error between a cubic-spline and the model and \acrshort{e50} measures the median error between the spline and the model. 
    These measured on both the train and test sets of the collected data, with the latter being denoted ``Test''.}
\label{tab:aft_summary}
\begin{tabular}{lrrrrrrrr}
\toprule
             & AIC              & BIC & Conc & Test Conc & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull      & $-2.11\cdot10^4$ & $-2.11\cdot10^4$ & 0.84 & 0.83 & 0.00 & 0.01 & 0.00 & 0.00 \\
Log Logistic & $-2.18\cdot10^4$ & $-2.18\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.01 & 0.00 & 0.00 \\
Log Normal   & $-2.25\cdot10^4$ & $-2.25\cdot10^4$ & 0.84 & 0.83 & 0.01 & 0.00 & 0.00 & 0.00 \\
\bottomrule
\end{tabular}
\end{table}
\begin{figure*}[tph!]
    \centering
        \includegraphics[width=.49\linewidth]{plots/combined/weibull_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_logistic_qq.pdf}
        \includegraphics[width=.49\linewidth]{plots/combined/log_normal_qq.pdf}
    \caption{The red and blue lines depict the relationship between the modelled number of failures (x-axis) and the measured number of failures (y-axis) for the training set (blue) and test set (red). The dotted line indicates a cubic spline fit to $S_{\theta}(t=t_a) \approx \lambda_{adv} $. A model that fits this cubic spline exactly would be a diagonal line at $y=x$. The process of comparing the fitted AFT model to a default cubic spline is called \textit{survival probability calibration} and is discussed in more detail in Section~\ref{best-fit}.}
    \label{fig:qq}
\end{figure*}
